\hypertarget{namespacefinal__assignment}{}\section{final\+\_\+assignment Namespace Reference}
\label{namespacefinal__assignment}\index{final\+\_\+assignment@{final\+\_\+assignment}}


This node is in charge of monitoring the state of the robot, and activate the corresping services and behaviour.  




\subsection{Detailed Description}
This node is in charge of monitoring the state of the robot, and activate the corresping services and behaviour. 

This node is used from bug algoritmh for behaviour wall follow.

This node implements the wall follower algoritm for navigation.

This node implements the user interface used by the bug algoritm.

This node implements the go to point behaviour for the bug algoritm.

This node implements the bug algoritm for navigation.

This node implements the main user interface.

As already said this node activates the corresponding services via the function change\+\_\+state(state), and for the first two behaviours it sets the new goal position with the function \hyperlink{namespacebig__brain_a4f091a106e4ba678afd9bc2df4f2789b}{new\+\_\+goal()}.

It\textquotesingle{}s used to manage the output on shell when the bug algoritm is N\+OT active

It\textquotesingle{}s used to manage the output on shell when the bug algoritm is activated

It works specifically when the bug algoritm is active

It works specifically when the bug algoritm is N\+OT active

the code is the same of \hyperlink{wall__follower__service_8py}{wall\+\_\+follower\+\_\+service.\+py} the comment are the same 